Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added other U(1) tunings to teh draft..

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
% - plots for different U(1)' charge

@@

@@

Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
the E$_6$SSM looks more fine tuned than the MSSM this is depends on
the cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained
version of the E$_6$SSM, with the cuttoff at the GUT scale, is
considered and there the cE$_6$SSM was found to be less tuned than the
cMSSM. Since a 125 GeV Higgs can be achieved in the E$_6$SSM with
ligher stops, then if the cutoff is large, the larger stop masses can
make that model more fine tuned due to large RGE effects.

>>>>

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig.~\ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
% - plots for different U(1)' charge

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{5cm}{%
\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
\resizebox{!}{5cm}{%
\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
\resizebox{!}{5cm}{%
\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}

@@

Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
the E$_6$SSM looks more fine tuned than the MSSM this depends on the
cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained version
of the E$_6$SSM, with the cuttoff at the GUT scale, is considered and
there the cE$_6$SSM was found to be less tuned than the cMSSM. Since a
125 GeV Higgs can be achieved in the E$_6$SSM with ligher stops, then
if the cutoff is large, the larger stop masses of the MSSM can make
that model more fine tuned due to large RGE effects.
